---
title: "case_study_bellabeat"
author: "Christopher Vroman"
date: "2023-10-23"
output: html_document
---
## Introduction to Bellabeat

Urška Sršen and Sando Mur founded Bellabeat, a high-tech company that 
manufactures health-focused smart products. Sršen used her background as an 
artist to develop beautifully designed technology that informs and inspires 
women around the world. 
Collecting data on activity, sleep, stress, and reproductive health has allowed 
Bellabeat to empower women with knowledge about their own health and habits. 
Since it was founded in 2013, Bellabeat has grown rapidly and quickly
positioned itself as a tech-driven wellness company for women.
By 2016, Bellabeat had opened offices around the world and launched 
multiple products. Bellabeat products became available

Products
○ Bellabeat app: The Bellabeat app provides users with health data related to 
their activity, sleep, stress,menstrual cycle, and mindfulness habits. 
This data can help users better understand their current habits and make 
healthy decisions. The Bellabeat app connects to their line of smart wellness 
products.

○ Leaf: Bellabeat’s classic wellness tracker can be worn as a bracelet, 
necklace, or clip. The Leaf tracker connects to the Bellabeat app to track 
activity, sleep, and stress.

○ Time: This wellness watch combines the timeless look of a classic timepiece 
with smart technology to track user activity, sleep, and stress. The Time watch 
connects to the Bellabeat app to provide you with insights into your 
daily wellness.

○ Spring: This is a water bottle that tracks daily water intake using smart 
technology to ensure that you are appropriately hydrated throughout the day. 
The Spring bottle connects to the Bellabeat app to track your hydration levels.

Source for this analysis https://www.kaggle.com/datasets/arashnic/fitbit/data

```{r install packages}
install.packages("tidyverse")
library(tidyverse)
install.packages("dplyr")
library(dplyr)
install.packages("ggplot2")
library(ggplot2)
```

## Business Task

Analyze the usage of non-Bellabeat smart devices and how those insights can be applied to Bellabeat smart devices.

```{r loading the CSV files }
daily_activity <- read.csv("dailyActivity_merged.csv")

weight_info <- read.csv("weightLogInfo_merged.csv")
```

## Exploring a few key tables

```{r}
head(daily_activity)

colnames(daily_activity)

head(weight_info)

colnames(weight_info)

n_distinct(daily_activity$Id)
n_distinct(weight_info$Id)

nrow(daily_activity)
nrow(weight_info)
```

## Summarizing some of statistics

A common aspect between the tables are the Id of the users

```{r}
daily_activity %>%
  select(TotalSteps,
         TotalDistance,
         Calories) %>%
  summary()

weight_info %>%
  select(WeightPounds,
         BMI) %>%
  summary()
```




## Plotted Points 


```{r tablets plotted separatley}
ggplot(data=daily_activity, aes(x=TotalSteps, y=Calories))+
  geom_point()+
  labs(title="Total Steps vs Calories")

ggplot(data=weight_info, aes(x=WeightPounds,y=BMI))+
  geom_point()+
  labs(title="WeightPounds vs BMI")

```

## Merging the Two tables
Merging the two tables can show how more steps can help with weight

```{r}
combined_data <- merge(weight_info, daily_activity, by="Id")

n_distinct(combined_data$Id)

ggplot(data=combined_data, aes(x=TotalSteps, y=WeightPounds))+
  geom_point()+
  labs(title="Total Steps vs WeightPounds")
```

